Reconstructing the last known movements of one of Nature's giants

### 2017-06-23 manuscript/blue-whale-ms.tex
Add CT edits to paragraph 7/8 main text

Blue whales were the first species that humans legislated to save, and represent a big conservation success story, although North Atlantic stocks have not recovered to the same extent as other whales in the region\cite{sigurjonsson1995life,pike2009note}. 
There is also evidence that blue whales are shifting their ranges due to warming waters off Iceland\cite{10.3389/fevo.2015.00006}. 
Thus understanding historical movements of North Atlantic blue whales has never been more vital if we wish to preserve them for future generations.

In conclusion, the model we present here allows us to recreate individual-level movement behaviours and life history using tissues from museum collections and other sources. 
This has applications beyond this individual whale, and beyond cetaceans, as our model can be applied to any marine species with constantly growing tissues, for example seal whiskers, shark skin, and fish scales. 
These techniques can also allow us study extinct species' behaviours and understand how populations were affected by past pressures such as hunting, and present-day pressures such as global change. 
Finally, our results highlight that museums represent a vast, mostly untapped, treasure trove of information ready for us to explore.

>>>>

This is the first quantitative evidence of historical individual-level movement behaviours in blue whales. 
Our novel simulation modelling removes a long-standing limitation in stable isotope ecology, and can be applied to stable isotope records from any incrementally-grown tissue to estimate most likely individual movement behaviours over multiple years. 
Such techniques can also be applied to extinct species' behaviours and understanding how populations were affected by past pressures such as hunting, and present-day pressures such as global change. 
Finally, our results highlight that museums represent a vast, mostly untapped, source of individual-level spatial ecology information.
